First and foremost I would like to express my deepest appreciation to my supervisor, Prof. Steve Furber, for all his contributions of time, patience, ideas and funding to my study.
%It has been a great honour to be his student, and my study has been such a unique experience.
I am grateful for his `ease-the-grip' strategy that I have complete freedom to explore my own research problems and find out solutions to them.
Although sometimes problems occur and tough time comes, he tells and encourages me, persistence is the key to all the problems.
It builds up my confidence to think and act professionally like a scientist.
At the same time, he knows when to `hold hands firmly' that the thesis would not be finished without his kind reminders about commitment on writing.

I would like to thank my colleagues John Woods, Cameron Patterson, Garibaldi Pineda Garcia, Yunhua Chen, Jonathan Heathcote and Robert James, for their collaborations, meaningful discussions, insightful comments and helpful English revisions on my papers and thesis.
Those sleepless nights we work towards deadlines, and the colourful and densely packed corrections on my printed papers will stay in my memory.

In addition, I express my gratitude to Cameron Patterson, Evangelos Stromatias, Mireya Lopez, Guangda Zhang, Garibaldi Garcia, Gengting Liu, Athanasios Stratikopoulos, and Crefeda Rodrigues for being my great companions and friends.
My study would not be such an enjoyable experience without them, since they always celebrate any achievement I have made, pull me out of stress and negative moods towards the bright side, and share the bitter-sweets on the journey to our PhD.

My sincere thanks to my parents and beloved husband, Xuekai Li and long-time friends Jingjing Cui and Xiaowen Jia for supporting and understanding me spiritually throughout my life in general.
I cannot be who I am without being part of their lives.
Especially with my husband, we take the adventure to Manchester, learn about the world, understand ourselves and pursue the meaning of life together.
My special thanks to him again. 
 
 	